Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-08-01 src/tex/ms.tex
Update ms.tex
Update list

1 Introduction\\
1.1 Motivation\\
1.1.1 GR broke down at some scale, find a new theory

2 Method

3 Results

4 Discussion\\
4.1 Limitation\\
4.1.1 orientation of detector (polarisations)\\
4.1.2 sensitivity of detector

4.2 Future Study\\
4.2.1 Data from better detector

>>>>

\begin{enumerate}
    \item Introduction
    \begin{enumerate}
        \item Motivation
        \begin{enumerate}
            \item GR broke down at some scale, find a new theory
            \item CS: beyond-GR theory
            \item test CS property (GW amplitude birefringence)
            \item GW have 2 polarisations
            \item GR: polarisation ratio depends on iota
        \end{enumerate}
    \end{enumerate}
    \item Method
    \begin{enumerate}
        \item
    \end{enumerate}
    \item Results
    \begin{enumerate}
        \item GW150914
        \begin{enumerate}
            \item
        \end{enumerate}
        \item GWTC-3
        \begin{enumerate}
            \item
        \end{enumerate}
    \end{enumerate}
    \item Discussion
    \begin{enumerate}
        \item Limitation
        \begin{enumerate}
            \item orientation of detector (polarisations)
            \item sensitivity of detector
        \end{enumerate}
        \item Future Study
        \begin{enumerate}
            \item Data from better detector
        \end{enumerate}
    \end{enumerate}
\end{enumerate}
